### 2017-12-10 CO681-QuantumInformationProcessing/project/quantum-primitives.tex
starting minima finding

>>>>

Consider the following {\it minima finding } problem, wherein we try to find $d$ smallest values of different types. We are give two functions: an objective $f: \{1, \dots, N\} \rightarrow \N \cup \{\infty\}$, and a type $g: \{1, \dots, N\} \rightarrow \N$. Let $|g| := | \{ g(i): i \in \{1,\dots, N\}\}|$. We are also given an integer $d \in \{, \dots, \min\{|g|, N\}\}$, and are to find $I \subseteq \{1, \dots, N\}$ such that:
\begin{itemize}
\item $|I| = d$,
\item $g(i) \neq g(j)$ for all $i,j \in I$ with $i\neq j$,
\item and for all $j \in \{1,\dots, N\}\backslash I$ and $i \in I$, if $f(j) < f(i)$ then there exists some $i' \in I$ such that $g(i') = g(j)$ and $f(i') \leq f(j)$.
\end{itemize}
